\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/iteration1.tex
created sui2014 dir
fixed figure width problem
iteration1.tex: added comment regarding user quotations

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1a.pdf}
\caption{Boxplot of target acquisition time for {\em IR selection} and {\em list selection} is shown on the left. The center of each box is the median value, while we annotate the mean value using white dashed lines. The cumulative distributions are shown on the right.}
\label{fig:ir_vs_list}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1.09\columnwidth]{figures/result_study1b.pdf}
\caption{Boxplot and CDF of target acquisition time when refinement is needed or not in {\em IR selection}}.
\label{fig:with_without_refinement}
\end{figure}

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, list selection was perceived to be cumbersome. One user noted benefit of {\em IR selection} being \studyquote{more direct [than list mode]}, allowing users to focus on the targeted objects instead of the screen. One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}, and many participants compared the overall time of target acquisition. One subject pointed out that \studyquote{{\em IR selection} doesn't requires you to swipe a lot of times like list mode}.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1a.pdf}
\caption{Boxplot of target acquisition time for {\em IR selection} and {\em list selection} is shown on the left. The center is the median value, and the mean value is shown using white dashed lines. The cumulative distributions are on the right.}
\label{fig:ir_vs_list}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1b.pdf}
\caption{Boxplot and CDF of target acquisition time when refinement is needed or not in {\em IR selection}}.
\label{fig:with_without_refinement}
\end{figure}

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, list selection was perceived to be cumbersome. One user noted benefit of {\em IR selection} being \studyquote{more direct [than list mode]}, allowing users to focus on the targeted objects instead of the screen. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}, and many participants compared the overall time of target acquisition. One subject pointed out that \studyquote{{\em IR selection} doesn't requires you to swipe a lot of times like list mode}.
